Handling Recursion in Generic Programming Using Closed Type Families

### 2018-05-14 lncs-paper.tex
+ acknowledgements

>>>>

\section*{Acknowledgments}
\label{sec:acks}

We are grateful to Julia Belyakova who helped to proof-read certain parts of the paper, 
and to the participants of the Seminar on Programming Languages and Compilers at 
I.I.~Vorovich Institute of Mathematics, Mechanics and Computer Science (Southern Federal
University, Russia) where we presented partial results of the work and got valuable feedback.

This project has received funding from the European Research Council (ERC) under the
European Union's Horizon 2020 research and innovation programme (grant agreement No 695412).
